---
html_document:
    toc: true
title: "Google Flights QPX Express API Wrapper in R"
---

```{r setup, echo=FALSE, warning=FALSE,cache=FALSE,results='hide'}
source('/media/roberto/Main Storage/Documents/bertplot/R/source/common_rmd_options.R')
```

# Motivation

QPX Express API offers global airline pricing in a single, standard API.  You can search it and get data on flight prices across lots of different carriers.

# Installation

```{r, eval=FALSE,results='hide'}
devtools::install_github('rweyant/googleflights')
```

# Basic Usage

First, you need to get an [API Key](https://developers.google.com/qpx-express/).
```{r, eval=FALSE}
library(googleflights)

# Set API key in a place all the functions have access to
set_apikey(YOUR_APIKEY)
```

# Get basic data

```{r,eval=FALSE}
result <- search(origin='DTW',dest='SFO',startDate='2016-03-01',endDate='2016-03-08')
```

The API returns data in JSON format.  The `search` function will parse it with `fromJSON.` This will return a list of lists.  

<a href="#top">Back to top</a>

# More Resources
- [Source as RMarkdown](https://github.com/rweyant/bertplot/blob/master/R/tutorials/googleflights-api/googleflights-api.Rmd)
- [Package Source on Github](https://github.com/rweyant/googleflights)
- [QPX Express API Documentation](https://developers.google.com/qpx-express/v1/)


```{r, echo=FALSE,fig.height=1,fig.width=2,fig.align='left'}
suppressWarnings(suppressPackageStartupMessages(library(png)))
suppressPackageStartupMessages(library(grid))
img <- readPNG('googleflights.png')
grid.raster(img)
```
